Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-12-08 doc/JFLA2022/Slides/Slides.tex
add coq-equations
a few more slides

@@

@@

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \maketitle
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Coq-community}
  \begin{block}{Objectives}
    \begin{itemize}
    \item
    \item
      \item Documentation on libraries
    \end{itemize}
  \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{What hydras are talking about?}
  \begin{block}{Hydra battles}
    \begin{itemize}
\item  \textcolor{mathcolor}{ordinals},
    \textcolor{mathcolor}{rapidly growing functions},
    \textcolor{mathcolor}{primitive recursive functions}, etc.
    \item \textcolor{coqstylecolor}{dependently typed functions},
      \textcolor{coqstylecolor}{proofs of well-foundedness},
         \textcolor{coqstylecolor}{impossibility proofs},
    \textcolor{coqstylecolor}{uniqueness of identity proofs (UIP)},
      \textcolor{coqstylecolor}{indefinite description (Hilbert's epsilon operator)},
    etc.
    \item \textcolor{plugincolor}{ackermann (Russel O'Connor)},
      \textcolor{plugincolor}{gaia (Jos\'e Grimm)},
    \end{itemize}

  \end{block}

>>>>

\usepackage{xspace}

\newcommand{\TODO}[2][]{[\textcolor{red}{TODO (#1):} \emph{#2}]}
\newcommand{\coq}{Coq\xspace}
\newcommand{\coqdoc}{Coqdoc\xspace}
\newcommand{\coqmakefile}{\texttt{coq\_makefile}\xspace}
\newcommand{\community}{Coq-community\xspace}
\newcommand{\gaia}{Gaia\xspace}
\newcommand{\alectr}{Alectryon\xspace}
\newcommand{\equations}{Equations\xspace}
\newcommand{\Hydras}{Hydras \& Co$\text.$\xspace}
\newcommand{\make}{\texttt{make}\xspace}

@@

\usepackage{ifpdf}
\ifpdf
\usepackage{graphicx}
%\usepackage{aeguill}
\else
\usepackage[dvips]{graphicx}
\fi

@@

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \maketitle
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Coq-community}
  \begin{block}{Objectives}
    \begin{itemize}
    \item \TODO{}{}
    \item\TODO{}{}
      \item Documentation on libraries
    \end{itemize}
  \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Yet another book on \coq?}
  \begin{block}{Kinds of books}
    \TODO{}{}
  \end{block}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Example-driven books}
  \begin{block}{Tsukuba Coq User's Group}
    Regular languages, lambda-calculus, programming language semantics, \dots

   \includegraphics[height=35mm]{tsukubabooks.jpg}
   %\includegraphics[height=45mm]{leaflet.jpg}
     \end{block}
     \begin{block}{\Hydras}
       Kirby \& Paris'  hydra battles, exponentiation algorithms, \dots?
     \end{block}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{What hydras are talking about?}
  \begin{block}{}
    \Hydras presents a consistent set of examples, which allow us to formalize 
    \textcolor{mathcolor}{Discrete math}, discuss
    \textcolor{coqstylecolor}{\coq style, specification and proof patterns}, and use  \textcolor{plugincolor}{a few plug-ins}.
  \end{block}
  \begin{block}{Hydra battles}
    \begin{itemize}
\item  \textcolor{mathcolor}{ordinals},
    \textcolor{mathcolor}{rapidly growing functions},
    \textcolor{mathcolor}{primitive recursive functions}, etc.
    \item \textcolor{coqstylecolor}{dependently typed functions},
      \textcolor{coqstylecolor}{proofs of well-foundedness},
         \textcolor{coqstylecolor}{impossibility proofs},
    \textcolor{coqstylecolor}{uniqueness of identity proofs (UIP)},
      \textcolor{coqstylecolor}{indefinite description (Hilbert's epsilon operator)},
    etc.
  \item
 \textcolor{plugincolor}{equations (Matthieu Sozeau)},
    \textcolor{plugincolor}{ackermann (Russel O'Connor)},
      \textcolor{plugincolor}{gaia (Jos\'e Grimm)}
    \end{itemize}
  \end{block}
